NGO analysis

### 2022-07-29 Dashboard/NGO Analysis dashboard alpha v003.Rmd
Commenting.

```{r sidebar}
# HTML
fileInput("html", label = "Upload html file", accept = ".html")

@@

# Excel
fileInput("excel", "Upload Excel file", accept = ".xlsx")

>>>>

```{r sidebar}
# HTML upload
fileInput("html", label = "Upload html file", accept = ".html")

@@

# Excel upload
fileInput("excel", "Upload Excel file", accept = ".xlsx")
